# Course Project
In this project, our goal is to use data from accelermoeters on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. We will predict the manner in which they did the exercise.

## About data
The [training data](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv)  and the  [test data](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv)  for this project come from this source: http://groupware.les.inf.puc-rio.br/har.

## Preprocess
load the data and clean them.
```{r cache=TRUE}
rm(list=ls())
data.training <- read.csv("pml-training.csv", header=T, stringsAsFactors=F)
data.testing <- read.csv("pml-testing.csv", header=T, stringsAsFactors=F)
# convert the predict variable "classe" to factor
data.training$classe <- as.factor(data.training$classe)

# remove columns that all values are NA in the data.testing
feature.num <- dim(data.testing)[2]
test.item.num <- dim(data.testing)[1]
keep.cols <- c()
for (i in 2:feature.num) { # exclude the first(X) feature
  if (sum(is.na(data.testing[,i])) != test.item.num) {
    keep.cols <- c(keep.cols, i)
  }
}
data.training <- data.training[, keep.cols]
data.testing <- data.testing[, keep.cols]
# drop feature: raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp
drop.cols <- c('raw_timestamp_part_1', 'raw_timestamp_part_2', 'cvtd_timestamp')
data.training <- data.training[, !(names(data.training) %in% drop.cols)]
data.testing <- data.testing[, !(names(data.testing) %in% drop.cols)]
```

## Split the data into training set and testing set
We split the data to get a training set(60%) and a testing set(40%)
```{r cache=TRUE}
library(caret)
set.seed(1024)
inTrain <- createDataPartition(data.training$classe, p=0.6, list=F)
training <- data.training[inTrain,]
testing <- data.training[-inTrain,]
```

## Training a fit model
We here using random forest with 3 times cross validation and then choose a best model.
```{r echo=TRUE, cache=TRUE, warning=FALSE}
set.seed(1024)
ctrl <- trainControl(method='cv', repeats=5)
modelFit <- train(classe ~ ., data = training, method='rf', trControl=ctrl)
modelFit
modelFit$finalModel
```
According the cross validation result, we choose the model which mtry=30. This model's in sample accuracy is almost 100%.

## Out of sample error
We using the 40% left testing set to calculate the out of sample error.
```{r echo=TRUE, cache=TRUE, warning=FALSE}
test.result <- predict(modelFit, newdata=testing)
confusionMatrix(test.result, testing$classe)
```
The out of sample accuracy is 99.7%, which means the out of sample error is about 0.3%.

## Predict the value
Using the model to generate result of the 20 submit records.
```{r}
ans <- predict(modelFit, newdata=data.testing)

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(ans)
```